---
title: "hw6"
author: "Keyi Wang"
date: "11/20/2019"
output: github_document
---

```{r setup, include=FALSE}
set.seed(10)

# load library
library(tidyverse)
library(viridis)
library(ggridges)
library(patchwork)
library(rvest)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  # display the code in the code truck above its results in the final document
  echo = TRUE,
  # do not display any warning messages generated by the code
  warning = FALSE,
  # set the figure to be 8 x 6, and the proportion it takes to be 90%
  fig.width = 8,
  fig.height = 6, 
  out.width = "90%"
)

# setting a global options for continuous data color family and a different format to set discrete data to have a color family
options(
  ggplot2.countinuous.colour = "viridis",
  ggplot2.countinuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

# have a minimal theme and legends at the bottom
theme_set(theme_get() + theme(legend.position = "bottom"))
```
# Problem 1-part1

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.)
```{r}
birthweight = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names()  %>%
   mutate(
    babysex = as.factor(case_when(
       babysex == 1 ~ "male",
       babysex == 2 ~ "female",
    )),
    frace = as.factor(case_when(
      frace == 1 ~ "White",
      frace == 2 ~ "Black",
      frace == 3 ~ "Asian",
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other",
      frace == 9 ~ "Unknown",
    )),
    malform = as.factor(case_when(
      malform == 0 ~ "absent",
      malform == 1 ~ "present"
    )),
    mrace = as.factor(case_when(
      mrace == 1 ~ "White",
      mrace == 2 ~ "Black",
      mrace == 3 ~ "Asian",
      mrace == 4 ~ "Puerto Rican",
      mrace == 8 ~ "Other",
    ))
  )
  
```



Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.
```{r}
hypo_model = function(df) {
  lm(bwt ~ bhead + blength + delwt + menarche , data = df)
}

weight_model = hypo_model(birthweight)

  
birthweight %>% 
  add_predictions(weight_model) %>% 
  add_residuals (weight_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
    geom_point(alpha = 0.3,color = "orange") +
  labs (
        title = "Hypothesized Regression Model: Predicted Values vs Residuals",
        x = "Predicted Values",
        y = "Residuals"
      )

```
Since we want to build a model based on baby birthweight, I decided to choose several predictors that are quite relavent to baby birthweight, which are baby’s head circumference at birth, baby's length, mother’s weight at delivery and mother’s age at birth. 
As we can see in the above graph, there is a heavy cluster in the lower right corner, with a tail fanning out to the top left, which suggests that my model is not great. The residuals do not form a desired straight line across the range of the predicted values 

# part 2 
Compare your model to two others:
One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r}

model_1 = function(df) {
  lm(bwt ~ blength + gaweeks, data = df)
}

model_2 = function(df) {
  lm(bwt ~ bhead + blength + babysex +
       (bhead * blength) + (bhead * babysex) + (blength * babysex) +
       (bhead * blength * babysex), data = df)
}


## cross validation, split data and run three models on each split

set.seed(10)

cv_birthweight = 
  crossv_mc(birthweight, 100) 

cv_birthweight = 
  cv_birthweight %>% 
  mutate(hypo_model = map(train, hypo_model),
         model_1 = map(train, model_1),
         model_2 = map(train, model_2)) %>% 
  mutate(rmse_hypo_model = map2_dbl(hypo_model, test, ~rmse(model = .x, data = .y)),
         rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
         rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)))


```

